Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-17 manuscript-figures.Rmd
R0 derivatives

# Sensitivity data for Topt
Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
    mutate(focal_var = factor(focal_var,
                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                           labels = c(
                             TeX("Adult lifespan"),
                             TeX("Biting frequency"),
                             TeX("Eggs per female per day"),
                             TeX("Immature development rate"),
                             TeX("Prob. of immature survival"),
                             TeX("Prob. of surviving EIP"),
                             TeX("Vector competence")
                           )
  ))

@@

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.ddTR0.rel.sens <- ddTR0.HPD %>%
  filter(KH %in% c(100) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $ddTR_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

Topt.HPD <- Topt.HPD %>%
  ungroup() %>%
  distinct() %>% 
  filter(!is.na(HPD_width)) %>% 
  pathosystem_labeller() %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
# arrange(sens_rel)

@@

plot.Topt.rel.sens <- Topt.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  # scale_y_continuous(
  #   limits = c(0,1)
  # ) +
  facet_wrap(~system_label) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

>>>>

# Sensitivity data for Topt
Topt.HPD <- read_rds("results/Topt_HPD_sens.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
    mutate(focal_var = factor(focal_var,
                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                           labels = c(
                             TeX("Adult lifespan"),
                             TeX("Biting frequency"),
                             TeX("Eggs per female per day"),
                             TeX("Immature development rate"),
                             TeX("Prob. of immature survival"),
                             TeX("Prob. of surviving EIP"),
                             TeX("Vector competence")
                           )
  ))

@@

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  # filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.ddTR0.rel.sens <- ddTR0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # filter(!(KH == 100 & sigmaH == Inf)) %>%
  # filter(rel_HPD_width != 0) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(
    # limits = Temp_range_for_plot,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $dR_0 / dT$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

@@

plot.Topt.rel.sens <- Topt.HPD %>% 
  ungroup() %>%
  distinct() %>% 
  filter(sigmaH == 100) %>% 
  filter(!is.na(HPD_width)) %>% 
  pathosystem_labeller() %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) %>% 
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  facet_wrap(~system_label) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

```{r fig-S10_2_dToptdKH_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_sens} The sensitivity of the thermal optimum to mosquito life history traits as a function of vertebrate host population density when $\\sigma_H = 50$.'}

dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_sens.rds") %>%
  ungroup() %>%
  distinct() %>% 
  filter(!is.na(HPD_width)) %>% 
  pathosystem_labeller() %>%
    mutate(focal_var = factor(focal_var,
                           levels = c("muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                           labels = c(
                             TeX("Adult lifespan"),
                             TeX("Biting frequency"),
                             TeX("Eggs per female per day"),
                             TeX("Immature development rate"),
                             TeX("Prob. of immature survival"),
                             TeX("Prob. of surviving EIP"),
                             TeX("Vector competence")
                           )
  )) %>% 
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all sensitivity values to get total sensitivity
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each sensitivity value by the total sensitivity
  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
# arrange(sens_rel)

plot.dToptdKH.rel.sens <- dToptdKH.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    # limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $ dT_{opt}/dK_H$ HPD width"))
  ) +
  facet_wrap(~system_label) +
  theme_minimal() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.dToptdKH.rel.sens)
```
